%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.3 (29/10/16)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com) with modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{casual} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{grey} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\usepackage[utf8]{inputenc}
\usepackage[scale=0.85]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\name{Nicolas}{Farabegoli} % Your last name

\email{nicolas.farabegoli@gmail.com}
%\email{nicolas.farabegoli2@unibo.it}
\homepage{nicolasfarabegoli.it}
\social[github]{nicolasfara}
%\quote{"A witty and playful quotation" - John Smith}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	CURRICULUM VITAE
%----------------------------------------------------------------------------------------

\makecvtitle

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cventry{2011--2016}{Technic high school}{ITT B. Pascal}{Cesena (FC), Italy}{}{Elettronics specializzation}
\cventry{2016--2020}{Bachelor degree}{Università di Bologna}{Cesena (FC), Italy}{\newline Ingegneria e Scienze Informatiche}{
    \begin{itemize}
        \item Thesis: Optimized implementation of Dirac's operator on GPGPU
        \item Supervisor: Moreno Marzolla
    \end{itemize}
}

\cventry{2021--Ongoing}{Master degree}{Università di Bologna}{Cesena (FC), Italy}{\newline Ingegneria e Scienze Informatiche}{Ongoing}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}

\cventry{Jun~2015--Aug~2015}{Embedded Systems Internship}{General System}{}{}{
    \begin{itemize}
        \item Developed a system for remote control of an embedded board.
        \item Developed and tested industrial switchboards.
        \item Developed access control based on RFID technology and Arduino.
    \end{itemize}
}

\section{Tutoring}

\cventry{Mar~2022--Sep~2022}{Algoritmi e Strutture Dati}{Università di Bologna}{Cesena (FC), Italy}{}{Module A-B}
\cventry{Mar~2021--Sep~2021}{Algoritmi e Strutture Dati}{Università di Bologna}{Cesena (FC), Italy}{}{Module B}

%------------------------------------------------
%   Projects
%------------------------------------------------

\section{Projects}

\cventry{Sep~2020--Mar~2021}{Unibo Motorsport}{Bologna (BO), Italy}{}{}{E-Powertrain division member}
\cventry{Jan~2016--Feb~2019}{CeSeNA Security Team}{Cesena (FC), Italy}{}{}{
    \begin{itemize}
        \item Active member
        \item Experience reverse engineering (binary reversing)
    \end{itemize}
}
\cventry{Sep~2014--Jul~2017}{FabLab Romagna}{Cesena (FC), Italy}{}{}{
During the period I developed several prototypes with Arduino and Raspberry, did team projects for events and exhibitions. I have also been involved in:
    \begin{itemize}
        \item Organization and improvement of the laboratory with new tools and equipment.
        \item Seminar ``Basic introduction to Electronics and it's components''
        \item Participation in the organization of the event \textit{Rimini Beach Mini Maker Faire} (2015).
    \end{itemize}
}

%----------------------------------------------------------------------------------------
%   COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\newpage

\section{Skills}

\cvitem{\textit{Self evaluation skill}}{
    \begin{itemize} % TODO(Improve those items)
        \item 1 --- \textit{Small exeprience, understand simple programs, make some changes to existing programs}
        \item 2 --- \textit{Medium experience, can write some line of code without any help}
        \item 3 --- \textit{Daily experience, can use some language feature without any help}
        \item 4 --- \textit{Advanced experience, can write idiomatic program with nontrivial throbleshooting}
        \item 5 --- \textit{Master experience, can write advanced and large scale programs with nontrivial behaviuors}
    \end{itemize}
}

\cvitem{Languages}{C/C++ (2), Java (4), Kotlin (3), Python (3), TypeScript (3), Scala (4), Ruby (1)}
\cvitem{Frameworks}{Cuda (2), Keras (1), Tensorflow (1)}
\cvitem{Utilities}{Git (4), Jupyter Notebook (2)}
\cvitem{Languages}{English, Italian}
\cvitem{O.S.}{GNU Linux, Mac, Windows}
\cvitem{Other}{3D Printer, PCB Designer, SMD assembler, CAD Designer}

%----------------------------------------------------------------------------------------
%   Open Source Contributions
%----------------------------------------------------------------------------------------

\section{Contribution to Open Source projects}
\cvitem{\href{https://github.com/atedeg/ecscala}{ECScala}}{Co-developer of the project and repo maintainer --- 2021.}
\cvitem{\href{https://github.com/nicolasfara/pfeeder}{pfeeder}}{Co-developer of the project and maintainer --- 2021.}
\cvitem{\href{https://gitlab.com/nic0lasfara/dirac-operator}{dirac-operator}}{Developed an optimized CUDA version of the Dirac operator --- 2019/20.}
\cvitem{\href{https://github.com/nicolasfara/oop17-fag}{fag}}{Co-developer of the project --- 2017.}


%----------------------------------------------------------------------------------------
%   INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Interests}

%\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists

\cvlistdoubleitem{MTB}{Walking}
\cvlistdoubleitem{Tennis}{Beach Tennis}
\cvlistdoubleitem{Hacking software and hardware}{Elettronics}
\cvlistdoubleitem{Open Source enthusiast and contributor}{Linux world}

\end{document}
